### 2015-07-20 rscripts/data_review.Rmd
notes about 3x3 plot
progress on panel figures

```{r, echo=FALSE}
source("munging.R")
setkey(breakoutDays(censor.dt[,
  user_id := .GRP, by=user_id
][,
  location_id := .GRP, by=location_id
]), login_day, login_time, logout_day, logout_time, user_id, location_id)
censor.dt
```

@@

ggplot(agg.final) + theme_bw() +
  aes(fill = factor(cluster), x = week, y = cum) + geom_area(position="fill") +
  ylab("prop. users by cluster") + labs(fill="cluster") +
  coord_cartesian(xlim=c(34, 300), ylim=c(0,1))

@@

>>>>

```{r, echo=FALSE}
source("munging.R")
zeroize(breakoutDays(censor.dt[,
  user_id := .GRP, by=user_id
][,
  location_id := .GRP, by=location_id
], login_day, login_time, logout_day, logout_time, user_id, location_id))
censor.dt
```

@@

ggplot(agg.final) + theme_bw() +
  aes(fill = factor(cluster), x = week, y = cum) + geom_area(position="fill") +
  ylab("prop. users by cluster") + labs(fill="cluster") +
  coord_cartesian(ylim=c(0,1))

@@

clustering locations:

 try categories of low, med, high usage rates
 vs short, med, long login times

 color vs y for membership

 locations that disappeared between intervals - add holes?

 rolling aggregration windows

 highlight changes by size (+alpha)?

```{r, echo=F}
duration_breaks <- censor.dt[,quantile(logout-login, probs=(1:2)/3)]
daily_login_breaks <- censor.dt[,.N,by=list(location_id, login_day)][,quantile(N,probs=(1:2)/3)] ## TODO zeros?
# for 90 day window
#  for extant locations
#   - what percent of active days fall in each login category?
#   - what percent of logins fall in each login category?
```
